Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-15 authors.tex

\textbf{Thomas Arildsen}$^{3}$\href{http://orcid.org/0000-0003-3254-3790}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Lorena Barba}$^{4}$\href{http://orcid.org/0000-0001-5812-2711}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Fabien C. Y. Benureau}$^{5}$\href{http://orcid.org/0000-0003-4083-4512}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{C. Titus Brown}$^{6}$\href{http://orcid.org/0000-0001-6001-2677}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Pierre de Buyl}$^{7}$\href{http://orcid.org/0000-0002-6640-6463}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Ozan Çağlayan}$^{8}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Andrew Davison}$^{9}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Marc André Delsuc}$^{10}$\href{http://orcid.org/0000-0002-1400-5326}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Georgios Detorakis}$^{11}$\href{http://orcid.org/0000-0001-5891-1702}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Damien Drix}$^{12}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Pierre Enel}$^{13}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Benoît Girard}$^{14}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Emmanuelle Gouillart}$^{15}$\href{http://orcid.org/0000-0002-3869-9967}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Olivier Grisel}$^{16}$\href{http://orcid.org/0000-0002-8226-4012}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Olivia Guest}$^{17}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Matt Hall}$^{18}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Rafael Neto Henriques}$^{19}$,

@@

\textbf{Xavier Hinaut}$^{20}$\href{http://orcid.org/0000-0002-1924-1184}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Mehdi Khamassi}$^{21}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Almar Klein}$^{22}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Andrei Maksimov}$^{23}$,

@@

\textbf{Pietro Marchesi}$^{24}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Erwan Le Masson}$^{25}$,

@@

\textbf{Dan McGlinn}$^{26}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Owen Petchey}$^{27}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Hans Ekkehard Plesser}$^{28}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Timothée Poisot}$^{29}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Karthik Ram}$^{30}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Yoav Ram}$^{31}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Etienne Roesch}$^{32}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Cyrille Rossant}$^{33}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Vahid Rostami}$^{34}$,

@@

\textbf{Aaron Shifman}$^{35}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Joseph Stachelek}$^{36}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Marcel Stimberg}$^{37}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Adam Tomkins}$^{38}$,

@@

\textbf{Federico Vaggi}$^{39}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Guillaume Viejo}$^{40}$,

@@

\textbf{Julien Vitay}$^{41}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Anya Vostinar}$^{42}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Roman Yurchak}$^{43}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Tiziano Zito}$^{44}$\\

>>>>

\textbf{Frédéric Alexandre}$^{3\S}$\href{http://orcid.org/0000-0002-6113-1878}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Thomas Arildsen}$^{4\dagger}$\href{http://orcid.org/0000-0003-3254-3790}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Lorena Barba}$^{5\dagger}$\href{http://orcid.org/0000-0001-5812-2711}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Fabien C. Y. Benureau}$^{6\ddagger}$\href{http://orcid.org/0000-0003-4083-4512}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{C. Titus Brown}$^{7\dagger}$\href{http://orcid.org/0000-0001-6001-2677}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Pierre de Buyl}$^{8\dagger}$\href{http://orcid.org/0000-0002-6640-6463}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Ozan Çağlayan}$^{9\ddagger}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Andrew Davison}$^{10\ddagger}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Marc André Delsuc}$^{11\ddagger}$\href{http://orcid.org/0000-0002-1400-5326}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Georgios Detorakis}$^{12\ddagger\S}$\href{http://orcid.org/0000-0001-5891-1702}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Damien Drix}$^{13\ddagger}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Pierre Enel}$^{14\ddagger}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Benoît Girard}$^{15\ddagger\S}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Emmanuelle Gouillart}$^{16\dagger}$\href{http://orcid.org/0000-0002-3869-9967}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Olivier Grisel}$^{17\ddagger}$\href{http://orcid.org/0000-0002-8226-4012}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Olivia Guest}$^{18\dagger}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Matt Hall}$^{19\ddagger}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Rafael Neto Henriques}$^{20\S}$,

@@

\textbf{Xavier Hinaut}$^{21\ddagger}$\href{http://orcid.org/0000-0002-1924-1184}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Mehdi Khamassi}$^{22\ddagger\S}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Almar Klein}$^{23\ddagger}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Andrei Maksimov}$^{24\S}$,

@@

\textbf{Pietro Marchesi}$^{25\ddagger}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Erwan Le Masson}$^{26}$,

@@

\textbf{Dan McGlinn}$^{27\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Christoph Metzner}$^{28\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Owen Petchey}$^{29\S}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Hans Ekkehard Plesser}$^{30\ddagger}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Timothée Poisot}$^{31\dagger}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Karthik Ram}$^{32\dagger}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Yoav Ram}$^{33\ddagger}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Etienne Roesch}$^{34\ddagger}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Cyrille Rossant}$^{35\ddagger}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Vahid Rostami}$^{36\S}$,

@@

\textbf{Aaron Shifman}$^{37\ddagger\S}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Joseph Stachelek}$^{38\S}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Marcel Stimberg}$^{39\ddagger}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Frank Stollmeier}$^{40\S}$\href{http://orcid.org/0000-0003-4858-0895}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Adam Tomkins}$^{41\ddagger}$,

@@

\textbf{Federico Vaggi}$^{42\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Guillaume Viejo}$^{43\S}$,

@@

\textbf{Julien Vitay}$^{44\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
\textbf{Anya Vostinar}$^{45\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
\textbf{Roman Yurchak}$^{46\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
\textbf{Tiziano Zito}$^{47\dagger}$\\
